Capacity and Utilization analysis of Toronto shelter(2024)

### 2024-09-27 paper/paper.qmd
Update and rename paper_Li.qmd to paper.qmd

With respect to the structure of this paper, @sec-data includes an overview of the data and @sec-model show the results of model; @sec-discussion includes a discussion of the results; and @sec-appendix includes supplementary information.

@@

# Result {#sec-model}

@@

# Plot the occupancy rate trend
ggplot(daily_occupancy_rate, aes(x = OCCUPANCY_DATE)) +
  geom_line(aes(y = Bed_Occupancy_Rate, color = "Bed Occupancy Rate"), size = 1) +
  geom_line(aes(y = Room_Occupancy_Rate, color = "Room Occupancy Rate"), size = 1, linetype = "dashed") +
  labs(title = "", x = "Date", y = "Occupancy Rate (%)") +
  theme_minimal() +
  scale_color_manual(values = c("Bed Occupancy Rate" = "blue", "Room Occupancy Rate" = "red")) +
  theme(legend.title = element_blank())
```
@fig-occupancy-rates shows the occupancy rates for beds and rooms in the shelter system over time. The blue line represents the bed occupancy rate, while the red line represents the room occupancy rate. Overall, the room occupancy rate (red) is higher and more stable, staying close to 100%. In contrast, the bed occupancy rate (blue) shows more fluctuations, generally ranging between 98% and 99%.

>>>>

With respect to the structure of this paper, @sec-data includes an overview of the data and show the results of model; @sec-discussion includes a discussion of the results; and @sec-appendix includes supplementary information.

@@

## analysis {#sec-data-analysis}

@@

# Plot the occupancy rate trend
ggplot(daily_occupancy_rate, aes(x = OCCUPANCY_DATE)) +
  geom_line(aes(y = Bed_Occupancy_Rate, color = "Bed Occupancy Rate"), size = 1) +
  geom_line(aes(y = Room_Occupancy_Rate, color = "Room Occupancy Rate"), size = 1, linetype = "dashed") +
  labs(title = "", x = "Date", y = "Occupancy Rate (%)") +
  theme_minimal() +
  scale_color_manual(values = c("Bed Occupancy Rate" = "blue", "Room Occupancy Rate" = "red")) +
  theme(legend.position = "top", legend.title = element_blank())
```
@fig-occupancy-rates shows the occupancy rates for beds and rooms in the shelter system over time. The blue line represents the bed occupancy rate, while the red line represents the room occupancy rate. Overall, the room occupancy rate (red) is higher and more stable, staying close to 100%. In contrast, the bed occupancy rate (blue) shows more fluctuations, generally ranging between 98% and 99%.
